---
title: "2021-07-18Tidy Tuesday Scooby Doo"
output: html_notebook
location: https://github.com/rfordatascience/tidytuesday/tree/master/data/2021/2021-07-13
---

#Load libraries
library(tidy)
library(readr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(RColorBrewer)

#get file
scoobydoo <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-13/scoobydoo.csv')


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

scooby_tv<- scoobydoo %>%
        filter(format == "TV Series")
        
scooby_tv$year        

, not_caught= if_else(caught_not == "TRUE", 1, 0),
         caught= if_else(caught_not == "FALSE", 1, 0))

```{r}
#Caught/Not Caught by Year
scooby_tv %>%
  mutate(year = year(date_aired)) %>%
  rename(not_caught = caught_not) %>%
  select(year,not_caught) %>%
  group_by(year ,not_caught) %>%
  summarise(n=n()) %>%
  ggplot(aes( x= year, y = n, fill =not_caught)) +
  scale_fill_brewer(palette = "Set2") +
  geom_col()+
  labs(title = "Scooby Doo Episodes Where Suspect is Caught & Year",
       subtitle = "Source: https://www.kaggle.com/williamschooleman/scoobydoo-complete", 
       x = "Year Aired", y = "Number of Episodes") 
```
#find the color-blind friendly pallettes
display.brewer.all(colorblindFriendly = T)


```{r}
#Which Character Caught the Bad Guy?
scooby_tv %>%
  mutate(year = year(date_aired),
         who_caught = case_when(caught_fred == "TRUE" ~ "Fred",
                                caught_daphnie == "TRUE" ~ "Daphnie",
                                caught_velma == "TRUE" ~ "Velma",
                                caught_shaggy == "TRUE" ~ "Shaggy",
                                caught_scooby == "TRUE" ~ "Scooby",
                                caught_not == "TRUE" ~ "Not Caught",
                                TRUE ~ "Other")) %>%
  select(year, who_caught) %>%
  group_by(year ,who_caught) %>%
  summarise(n=n()) %>%
  ggplot(aes( x= year, y = n, fill =who_caught)) +
  scale_fill_brewer(palette = "Set2") +
  geom_col()+
  labs(title = "Who Caught the Bad Guy in Scooby Doo by Year",
       subtitle = "Source: https://www.kaggle.com/williamschooleman/scoobydoo-complete", 
       x = "Year Aired", y = "Number of Episodes") 
```

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

